IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-04-28 response.tex

		\begin{response}
			We sincerely apologize for the inconvenience. The figures have been amplified in the revised manuscript.
			\label{re:1.4}
		\end{response}

		\begin{point}
			In the current version, the authors claimed that by applying semidefinite relaxation and omitting the rank-one constraint, the performance loss is negligible. The reviewer wonders if this is because of the relatively simple system model, as there is only one single user who has both power and information requirements. It could be better if the authors can further discuss this issue for a more general multiple user scenario.
			\label{pt:1.5}
		\end{point}

		\begin{response}
			We agree with the reviewer that the relaxation on the rank-one constraint deserves more attention. However, as discussed in Response~\ref{re:1.2}, multi-user IRS-aided SWIPT is out the scope of this paper and we would like to provide some general ideas to address this issue. For any passive beamforming problem with non-convex unit-rank constraint, if the proof to Proposition~\ref{M-pr:relaxation} is unavailable, existing approaches include 1) relax the constraint and use Gaussian randomization method to obtain a high-quality solution \cite{M-Luo2010}, 2) replace the unit-rank constraint with the constraint on largest singular value $\mathrm{Tr}(\boldsymbol{\Phi})-\sigma_{\max} (\boldsymbol{\Phi}) \le 0$ then solve the problem by the penalty method \cite{M-Wu2020a}, \cite{Wu2021}, 3) apply the gradient descent in the manifold space \cite{Zuo2020}. All three techniques are expected to provide a unit-rank solution with performance very close to the original solution.
			\label{re:1.5}
		\end{response}
	\end{reviewer}

	\begin{reviewer}
		\begin{point}
			New RIS models are now being adopted as in \cite{M-Abeywickrama2020} where it has been shown that the reflected signals depend on the direction of the arriving signal and this needs to be included in the analysis for realistic quantification.
			\label{pt:2.1}
		\end{point}

		\begin{response}
			Thank you for sharing this paper. It investigated the impact of non-zero effective resistance on the reflection pattern and pointed out that the amplitude of the reflection coefficient depends on the phase shift forced on the incoming signal when power dissipation is considered at the IRS. It also proposed an analytical IRS model together with an BCD algorithm to maximize the achievable rate by passive beamforming. Simulation results emphasized the importance of modeling such a relationship in practical IRS design. There exist various refined models of IRS in the literature, however, we have finally decided to use the most common and simplest IRS model at the current stage to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT. We have mentioned in the conclusion that ``Also, the use of more involved IRS architecture based on direction- and frequency-dependent reflection \cite{M-Abeywickrama2020} and/or partially/fully-connected reflection \cite{M-Shen2020a} could be considered in future works.''
			\label{re:2.1}
		\end{response}

@@

			Fig.~\ref{fi:re_noise}--\ref{fi:re_reflector} demonstrate that the LC-BCD Algorithm~\ref{al:lc_bcd} achieves near-optimal performance under different configurations.

			\begin{figure}[!h]
				\centering
				\subfloat[Average noise power\label{fi:re_noise}]{
					\resizebox{0.45\columnwidth}{!}{
						\input{assets/re_noise.tex}
					}
				}
				\subfloat[AP-IRS horizontal distance\label{fi:re_distance}]{
					\resizebox{0.45\columnwidth}{!}{
						\input{assets/re_distance.tex}
					}
				}
				\\
				\subfloat[Transmit antennas\label{fi:re_tx}]{
					\resizebox{0.45\columnwidth}{!}{
						\input{assets/re_tx.tex}
					}
				}
				\subfloat[Reflecting elements\label{fi:re_reflector}]{
					\resizebox{0.45\columnwidth}{!}{
						\input{assets/re_reflector.tex}
					}
				}
				\caption{Average achievable R-E region under different configurations.}
			\end{figure}
			\label{re:2.7}
		\end{response}

		\begin{point}
			How practical is it to consider lossless reflection from the RIS? Specifically, by considering the magnitude to be 1, the reflection losses at the RIS have been ignored.
			\label{pt:2.8}
		\end{point}

		\begin{response}
			The assumption of lossless reflection is indeed ideal but common in microwave theory (e.g., \cite{Shen2020a}). Based on the circuit analysis, the authors of \cite{M-Abeywickrama2020} shows that the reflection amplitude depends on the phase shift, which is minimized at \num{0} phase shift and is negatively correlated to the element resistance. For $R_l=\SI{1}{\ohm}$, $\lvert{\phi_l}\rvert$ is \num{1} for $\theta_l=\pi$ but around \num{0.6} for $\theta_l=\num{0}$. From the perspective of field and propagation, \cite{Ozdogan2020} points out that if the dimension of IRS element is much larger than the wavelength, the beamwidth would become small and the scattered field strength would depend on the observation angle. However, to reduce the design complexity and provide a preliminary insight, we considered the lossless reflection pattern at the IRS in this paper.
			\label{re:2.8}
		\end{response}

@@

		\begin{point}
			Minor comment: The size of all the numerical results figures is too small.
			\label{pt:2.9}
		\end{point}

		\begin{response}
			We sincerely apologize for the inconvenience. The figures have been amplified in the revised manuscript.
			\label{re:2.9}
		\end{response}
	\end{reviewer}

	\begin{reviewer}
		\begin{point}
			First of all, motivations of studying the IRS on SWIPT is very unclear to me. Please clarify.
			\label{pt:3.1}
		\end{point}

		\begin{response}
			We appreciate your suggestion and have modified the manuscript to emphasize this point. The major issue of WPT and SWIPT is the low harvested DC power. To increase it, boosting the harvester input power level would be very helpful. This is achieved by the IRS that can engineer the channels such that the power level at the receiver gets amplified, and the smart channel control and low power consumption of IRS are expected to bring more opportunities to SWIPT. A major challenge for SWIPT is that information decoding and energy harvesting have different sensitivity on the received signal. Although conventional radios as Wi-Fi and Bluetooth can support a signal strength of \num{-90} to \SI{-100}{\dBm}, most existing harvesters can only capture signals at \num{-20} to \SI{-30}{\dBm} power level. Since the transmit power is strictly constrained by government regulations, it is crucial to increase the end-to-end power transfer efficiency to boost the harvested power and extend the system coverage. Therefore, we believe the passive beamforming ability of the IRS can significantly enhance WPT and SWIPT performance.
			\label{re:3.1}
		\end{response}

@@

			\emph{Second}, we characterize each R-E boundary point by energy maximization under rate constraint, and solve the problem by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT). For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) even with rectifier nonlinearity. For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm and retrieve the IRS phase shift by eigen decomposition with optimality proof. Finally, the superposed waveform is optimized by the Geometric Programming (GP) technique. The IRS phase shift, active precoder, and waveform amplitude are updated iteratively until convergence. This is the first paper to jointly optimize waveform and active/passive beamforming in IRS-aided SWIPT.

			\emph{Third}, we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm. The Water-Filling (WF) strategy for modulated waveform and the SMF strategy for multisine waveform are combined in the time domain and power domain to facilitate practical SWIPT implementation. To accommodate the suboptimal waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio under TS mode and the combining and splitting ratios under PS mode. The proposed low-complexity designs achieve near-optimal R-E performance in different scenarios.

			\emph{Fourth}, we provide numerical results to evaluate the proposed algorithms. It is concluded that 1) multisine waveform is beneficial to energy transfer especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to the rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region, 7) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E tradeoff point and require adaptive designs, 8) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
			\label{re:3.2}
		\end{response}

### 2021-04-28 main.tex
:pencil: Update manuscript

			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the electromagnetic wave at a specific frequency to mitigate signal attenuation. Motivated by this, \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power. The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}. In \cite{Abeywickrama2019}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the dependency of the reflection amplitude on the phase shift for practical IRS. To estimate the cascaded AP-IRS-User Equipment (UE) link without RF-chains at the IRS, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}. The authors of \cite{Yang2020} considered a novel dynamic passive beamforming for Orthogonal Frequency-Division Multiplexing (OFDM) systems, where the reflection coefficient is varied over consequent time slots to enable flexible resource allocation over time-frequency Resource Blocks (RBs). In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
		\end{subsection}

@@

			\emph{Fourth}, we provide numerical results to evaluate the proposed algorithms. It is concluded that 1) multisine waveform is beneficial to energy transfer especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to the rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region, 7) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs, 8) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.

@@

		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the R-E region with different IRS strategies for narrowband and broadband SWIPT. The ideal Frequency-Selective (FS) IRS assumes the reflection coefficient of each element is independent and controllable at different frequencies. The adaptive IRS adjusts the passive beamforming for different R-E points by Algorithm~\ref{al:sca}. The WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:m_sca} then fixed for the whole R-E region (i.e., only vary the waveform amplitude and splitting ratio). The random IRS models the phase shift of all elements as i.i.d. uniform random variables over $[0, 2\pi)$. \emph{First,} random IRS and no IRS perform worse than other schemes since no passive beamforming is exploited. Their R-E boundaries coincide because the antenna mode reflection of the random IRS is canceled out after averaging over the channel realizations. \emph{Second,} the performance of ideal, adaptive and WIT/WPT-optimized IRS are similar when the bandwidth is small, while the adaptive IRS outperforms the WIT/WPT-optimized IRS but is worse than the ideal FS IRS when the bandwidth is large. In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes insignificant, and the auxiliary link can be roughly maximized at all subbands. It suggests that for narrowband SWIPT, the optimal passive beamforming for any R-E point is optimal for the whole R-E region, and the corresponding composite channel and active precoder are also optimal for the whole R-E region. On the other hand, since the information decoder and energy harvester prefer different power allocation in the frequency domain, the optimal IRS reflection coefficient varies at different R-E points for broadband SWIPT. By adaptive passive beamforming, the channel strength can be either amplified at the few strongest subbands to enhance the rate at low SNR, or spread evenly to boost the output DC power. It emphasizes the R-E advantage of adaptive passive beamforming design for broadband SWIPT.

@@

	\begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
		This paper investigated the R-E tradeoff of a single user employing practical receiving strategies in a novel IRS-aided multi-carrier MISO SWIPT system. Uniquely, we consider the joint waveform, active and passive beamforming design under rectifier nonlinearity to maximize the achievable R-E region. A three-stage BCD algorithm is proposed to solve the problem. In the first stage, the IRS phase shift is obtained by the SCA technique and eigen decomposition. In the second and third stages, the active precoder is derived in closed form, and the waveform amplitude and splitting ratio are optimized by the GP method. We also propose and combine closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm that achieves near-optimal performance. Numerical results reveal significant R-E gains by considering harvester nonlinearity in the passive beamforming design. Compared with active antennas, IRS elements cannot be designed independently at different frequencies but integrate coherent combining and equal gain transmission in a fully passive manner to boost the array gain and power scaling order. However, a large number of reflecting elements may be required to compensate the double fading in the auxiliary link.

        One particular unanswered question of this paper is how to design waveform, active and passive beamforming in a multi-user multi-carrier IRS-aided SWIPT system. Also, the use of more involved IRS architecture based on partially/fully-connected and/or direction- and frequency-dependent reflection could be considered in future works.
	\end{section}

@@

			By applying rank constraint relaxation, problem~\eqref{ob:irs_equivalent}--\eqref{co:irs_equivalent_sd} is convex w.r.t. $\boldsymbol{\Phi}$ and satisfies the Slater's condition \cite{Boyd2004}, thus strong duality holds. The corresponding Lagrangian function at iteration $i$ is given by \eqref{eq:lagrangian}, where $\mu$, $\boldsymbol{\nu}$, $\boldsymbol{\Upsilon}$ denote respectively the scalar, vector and matrix Lagrange multiplier associated with constraint~\eqref{co:irs_equivalent_rate}, \eqref{co:irs_equivalent_modulus} and \eqref{co:irs_equivalent_sd}, and $\zeta$ collects all terms irrelevant to $\boldsymbol{\Phi}^{(i)}$.
			\begin{figure*}[!b]
				\hrule
				\begin{flalign}\label{eq:lagrangian}
					\mathcal{L}
					&= \mathrm{tr}\left(\boldsymbol{\Phi}^{(i)}\right) - \frac{1}{2} \beta_2 \rho \mathrm{tr}\Bigl(
							(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
						\Bigr) - \frac{3}{8} \beta_4 \rho^2 \Biggl(
							4 t_{\mathrm{I},0}^{(i-1)} \mathrm{tr}\Bigl(
								\boldsymbol{C}_{\mathrm{I},0} \boldsymbol{\Phi}^{(i)}
							\Bigr) + \sum_{k=-N+1}^{N-1} 2 (t_{\mathrm{P},k}^{(i-1)})^* \mathrm{tr}\Bigl(
								\boldsymbol{C}_{\mathrm{P},k} \boldsymbol{\Phi}^{(i)}
							\Bigr)
							&&\nonumber\\
					&\quad+ 2 (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) \mathrm{tr}\Bigl(
								(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
							\Bigr) - \mathrm{tr}^2 \Bigl(
								(\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
							\Bigr)
						\Biggr) + \mu \Biggl(
						2^{\bar{R}} - \prod_{n=1}^N \biggl(
							1 + \frac{(1-\rho) \mathrm{tr}\Bigl(
								\boldsymbol{C}_n \boldsymbol{\Phi}^{(i)}
							\Bigr)}{\sigma_n^2}
						\biggr)
					\Biggr)&&\nonumber\\
					&\quad+ \mathrm{tr}\biggl(
						\mathrm{diag}(\boldsymbol{\nu}) \odot \Bigl(
							\boldsymbol{\Phi}^{(i)} \odot \boldsymbol{I} - \boldsymbol{I}
						\Bigr)
					\biggr) - \mathrm{tr} \Bigl(
						\boldsymbol{\Upsilon} \boldsymbol{\Phi}^{(i)}
					\Bigr) + \zeta.&&
				\end{flalign}
			\end{figure*}
			The Karush–Kuhn–Tucker (KKT) conditions on the primal and dual solutions are
			\begin{subequations}
				\begin{equation}\label{eq:lagrange_multiplier}
					\mu^\star \ge 0, \boldsymbol{\Upsilon}^\star \succeq \boldsymbol{0},
				\end{equation}
				\begin{equation}\label{eq:complementary_slackness}
					\boldsymbol{\nu}^\star \odot \mathrm{diag}^{-1}(\boldsymbol{\Phi}^\star) = \boldsymbol{0}, \boldsymbol{\Upsilon}^\star \boldsymbol{\Phi}^\star = \boldsymbol{0},
				\end{equation}
				\begin{equation}\label{eq:gradient}
					\nabla_{\boldsymbol{\Phi}^\star} \mathcal{L} = 0.
				\end{equation}
			\end{subequations}

			We then derive the gradient explicitly and rewrite \eqref{eq:gradient} as
			\begin{equation}
				\boldsymbol{\Upsilon}^\star = \boldsymbol{I} - \boldsymbol{\Delta}^\star
			\end{equation}
			where $\boldsymbol{\Delta}^\star$ is defied in \eqref{eq:delta}.
			\begin{figure*}[!b]
				\begin{flalign}\label{eq:delta}
					\boldsymbol{\Delta}^\star
					&= \frac{1}{2} \beta_2 \rho (\boldsymbol{C}_{\mathrm{I},0}+\boldsymbol{C}_{\mathrm{P},0}) + \frac{3}{4} \beta_4 \rho^2
						\Biggl(
							2 t_{\mathrm{I},0}^{(i-1)} \boldsymbol{C}_{\mathrm{I},0} + \sum_{k=-N+1}^{N-1} (t_{\mathrm{P},k}^{(i-1)})^* \boldsymbol{C}_{\mathrm{P},k} + (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) (\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0})&&\nonumber\\
					&\quad- (\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \mathrm{tr}\Bigl(
								(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^\star
							\Bigr)
						\Biggr) + \mu^\star \sum_{n=1}^N \frac{(1-\rho) \boldsymbol{C}_n}{\sigma_n^2} \prod_{n'=1,n' \ne n}^N \Biggl(
						1 + \frac{(1-\rho)\mathrm{tr}\Bigl(
							\boldsymbol{C}_{n'} \boldsymbol{\Phi}^\star
						\Bigr)}{\sigma_{n'}^2}
					\Biggr) - \mathrm{diag}(\boldsymbol{\nu^\star}).&&
				\end{flalign}
			\end{figure*}
			Note that \eqref{eq:complementary_slackness} suggests $\mathrm{rank}(\boldsymbol{\Upsilon}^\star)+\mathrm{rank}(\boldsymbol{\Phi}^\star) \le L+1$. By reusing the proof in Appendix A of \cite{Xu2020}, we conclude $\mathrm{rank}(\boldsymbol{\Upsilon}^\star) \ge L$. On the other hand, $\boldsymbol{\Phi}^\star$ cannot be zero matrix and $\mathrm{rank}(\boldsymbol{\Phi}^\star) \ge 1$. Therefore, any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed problem~\eqref{op:irs_equivalent} is rank-\num{1}. Due to the equivalence between \eqref{ob:irs} and \eqref{ob:irs_equivalent}, $\boldsymbol{\Phi}^\star$ is also optimal to the relaxed problem~\eqref{op:irs} and Proposition~\ref{pr:relaxation} holds.
		\end{subsection}

>>>>

			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the electromagnetic wave at a specific frequency to mitigate signal attenuation. Motivated by this, \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power. The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}. In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the dependency of the reflection amplitude on the phase shift for practical IRS. To estimate the cascaded AP-IRS-User Equipment (UE) link without RF-chains at the IRS, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}. The authors of \cite{Yang2020} considered a novel dynamic passive beamforming for Orthogonal Frequency-Division Multiplexing (OFDM) systems, where the reflection coefficient is varied over consequent time slots to enable flexible resource allocation over time-frequency Resource Blocks (RBs). In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
		\end{subsection}

@@

			\emph{Fourth}, we provide numerical results to evaluate the proposed algorithms. It is concluded that 1) multisine waveform is beneficial to energy transfer especially when the number of subbands is large, 2) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR, 3) there exist two optimal IRS development locations, one close to the AP and one close to the UE, 4) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements, 5) due to the rectifier nonlinearity, the output DC current scales quadratically with the number of transmit antennas and quartically with the number of IRS elements, 6) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region, 7) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E tradeoff point and require adaptive designs, 8) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.

@@

		Fig.~\ref{fi:re_irs_1mhz} and \ref{fi:re_irs_10mhz} explore the R-E region with different IRS strategies for narrowband and broadband SWIPT. The ideal Frequency-Selective (FS) IRS assumes the reflection coefficient of each element is independent and controllable at different frequencies. The adaptive IRS adjusts the passive beamforming for different R-E points by Algorithm~\ref{al:sca}. The WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:m_sca} then fixed for the whole R-E region (i.e., only vary the waveform amplitude and splitting ratio). The random IRS models the phase shift of all elements as i.i.d. uniform random variables over $[0, 2\pi)$. \emph{First,} random IRS and no IRS perform worse than other schemes since no passive beamforming is exploited. Their R-E boundaries coincide because the antenna mode reflection of the random IRS is canceled out after averaging over the channel realizations. \emph{Second,} the performance of ideal, adaptive and WIT/WPT-optimized IRS are similar when the bandwidth is small, while the adaptive IRS outperforms the WIT/WPT-optimized IRS but is worse than the ideal FS IRS when the bandwidth is large. In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes insignificant, and the auxiliary link can be roughly maximized at all subbands. It suggests that for narrowband SWIPT, the optimal passive beamforming for any R-E point is optimal for the whole R-E region, and the corresponding composite channel and active precoder are also optimal for the whole R-E region. On the other hand, since the channel frequency selectivity affects the performance of information decoder and energy harvester differently, the optimal IRS reflection coefficient varies at different R-E points for broadband SWIPT. By adaptive passive beamforming, the channel strength can be either amplified at the few strongest subbands to enhance the rate at low SNR, or spread evenly to boost the output DC power. It emphasizes the R-E advantage of adaptive passive beamforming design for broadband SWIPT.

@@

	\begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
		This paper investigated the R-E tradeoff of a single user employing practical receiving strategies in a novel IRS-aided multi-carrier MISO SWIPT system. Uniquely, we consider the joint waveform, active and passive beamforming design under rectifier nonlinearity to maximize the achievable R-E region. A three-stage BCD algorithm is proposed to solve the problem. In the first stage, the IRS phase shift is obtained by the SCA technique and eigen decomposition. In the second and third stages, the active precoder is derived in closed form, and the waveform amplitude and splitting ratio are optimized by the GP method. We also propose and combine closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm that achieves near-optimal performance. Numerical results reveal significant R-E gains by considering harvester nonlinearity in the passive beamforming design. Compared with active antennas, IRS elements cannot be designed independently across frequencies, but can integrate coherent combining and equal gain transmission in a fully passive manner to boost the array gain and power scaling order. However, a large number of reflecting elements may be required to compensate the double fading in the auxiliary link.

        One particular unanswered question of this paper is how to design waveform, active and passive beamforming in a multi-user multi-carrier IRS-aided SWIPT system. Also, the use of more involved IRS architecture based on direction- and frequency-dependent reflection \cite{Abeywickrama2020} and/or partially/fully-connected reflection \cite{Shen2020a} could be considered in future works.
	\end{section}

@@

			By applying rank constraint relaxation, problem~\eqref{ob:irs_equivalent}--\eqref{co:irs_equivalent_sd} is convex w.r.t. $\boldsymbol{\Phi}$ and satisfies the Slater's condition \cite{Boyd2004}, thus strong duality holds. The corresponding Lagrangian function at iteration $i$ is given by \eqref{eq:lagrangian}, where $\mu$, $\boldsymbol{\nu}$, $\boldsymbol{\Upsilon}$ denote respectively the scalar, vector and matrix Lagrange multiplier associated with constraint~\eqref{co:irs_equivalent_rate}, \eqref{co:irs_equivalent_modulus} and \eqref{co:irs_equivalent_sd}, and $\zeta$ collects all terms irrelevant to $\boldsymbol{\Phi}^{(i)}$.
			\begin{figure*}[!b]
				\hrule
				\begin{flalign}\label{eq:lagrangian}
					\mathcal{L}
					&= \mathrm{tr}\left(\boldsymbol{\Phi}^{(i)}\right) - \frac{1}{2} \beta_2 \rho \mathrm{tr}\Bigl(
							(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
						\Bigr) - \frac{3}{8} \beta_4 \rho^2 \Biggl(
							4 t_{\mathrm{I},0}^{(i-1)} \mathrm{tr}\Bigl(
								\boldsymbol{C}_{\mathrm{I},0} \boldsymbol{\Phi}^{(i)}
							\Bigr) + \sum_{k=-N+1}^{N-1} 2 (t_{\mathrm{P},k}^{(i-1)})^* \mathrm{tr}\Bigl(
								\boldsymbol{C}_{\mathrm{P},k} \boldsymbol{\Phi}^{(i)}
							\Bigr)
							&&\nonumber\\
					&\quad+ 2 (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) \mathrm{tr}\Bigl(
								(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
							\Bigr) - \mathrm{tr}^2 \Bigl(
								(\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
							\Bigr)
						\Biggr) + \mu \Biggl(
						2^{\bar{R}} - \prod_{n=1}^N \biggl(
							1 + \frac{(1-\rho) \mathrm{tr}\Bigl(
								\boldsymbol{C}_n \boldsymbol{\Phi}^{(i)}
							\Bigr)}{\sigma_n^2}
						\biggr)
					\Biggr)&&\nonumber\\
					&\quad+ \mathrm{tr}\biggl(
						\mathrm{diag}(\boldsymbol{\nu}) \odot \Bigl(
							\boldsymbol{\Phi}^{(i)} \odot \boldsymbol{I} - \boldsymbol{I}
						\Bigr)
					\biggr) - \mathrm{tr} \Bigl(
						\boldsymbol{\Upsilon} \boldsymbol{\Phi}^{(i)}
					\Bigr) + \zeta.&&
				\end{flalign}
			\end{figure*}
			The Karush–Kuhn–Tucker (KKT) conditions on the primal and dual solutions are
			\begin{subequations}
				\begin{equation}\label{eq:lagrange_multiplier}
					\mu^\star \ge 0, \boldsymbol{\Upsilon}^\star \succeq \boldsymbol{0},
				\end{equation}
				\begin{equation}\label{eq:complementary_slackness}
					\boldsymbol{\nu}^\star \odot \mathrm{diag}^{-1}(\boldsymbol{\Phi}^\star) = \boldsymbol{0}, \boldsymbol{\Upsilon}^\star \boldsymbol{\Phi}^\star = \boldsymbol{0},
				\end{equation}
				\begin{equation}\label{eq:gradient}
					\nabla_{\boldsymbol{\Phi}^\star} \mathcal{L} = 0.
				\end{equation}
			\end{subequations}
			We then derive the gradient explicitly and rewrite \eqref{eq:gradient} as
			\begin{equation}
				\boldsymbol{\Upsilon}^\star = \boldsymbol{I} - \boldsymbol{\Delta}^\star
			\end{equation}
			where $\boldsymbol{\Delta}^\star$ is defied in \eqref{eq:delta}.
			\begin{figure*}[!b]
				\begin{flalign}\label{eq:delta}
					\boldsymbol{\Delta}^\star
					&= \frac{1}{2} \beta_2 \rho (\boldsymbol{C}_{\mathrm{I},0}+\boldsymbol{C}_{\mathrm{P},0}) + \frac{3}{4} \beta_4 \rho^2
						\Biggl(
							2 t_{\mathrm{I},0}^{(i-1)} \boldsymbol{C}_{\mathrm{I},0} + \sum_{k=-N+1}^{N-1} (t_{\mathrm{P},k}^{(i-1)})^* \boldsymbol{C}_{\mathrm{P},k} + (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) (\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0})&&\nonumber\\
					&\quad- (\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \mathrm{tr}\Bigl(
								(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^\star
							\Bigr)
						\Biggr) + \mu^\star \sum_{n=1}^N \frac{(1-\rho) \boldsymbol{C}_n}{\sigma_n^2} \prod_{n'=1,n' \ne n}^N \Biggl(
						1 + \frac{(1-\rho)\mathrm{tr}\Bigl(
							\boldsymbol{C}_{n'} \boldsymbol{\Phi}^\star
						\Bigr)}{\sigma_{n'}^2}
					\Biggr) - \mathrm{diag}(\boldsymbol{\nu^\star}).&&
				\end{flalign}
			\end{figure*}
			Note that \eqref{eq:complementary_slackness} suggests $\mathrm{rank}(\boldsymbol{\Upsilon}^\star)+\mathrm{rank}(\boldsymbol{\Phi}^\star) \le L+1$. By reusing the proof in Appendix A of \cite{Xu2020}, we conclude $\mathrm{rank}(\boldsymbol{\Upsilon}^\star) \ge L$. On the other hand, $\boldsymbol{\Phi}^\star$ cannot be zero matrix and $\mathrm{rank}(\boldsymbol{\Phi}^\star) \ge 1$. Therefore, any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed problem~\eqref{op:irs_equivalent} is rank-\num{1}. Due to the equivalence between \eqref{ob:irs} and \eqref{ob:irs_equivalent}, $\boldsymbol{\Phi}^\star$ is also optimal to the relaxed problem~\eqref{op:irs} and Proposition~\ref{pr:relaxation} holds.
		\end{subsection}
